Open-source tools in R for landscape ecology

### 2020-12-20 paper/paper.Rmd
improved data provessing

A second common spatial data processing task is required when the available data extends over a larger area than the study region.
In this case, the pre-processing of spatial data can include vector clipping or raster cropping.
Related to that, also masking of certain areas of the study region can be required by using e.g. certain spatial filters such as water bodies.
Packages from Section \@ref(sec:spatrep) also allow for these operations.
Additionally, they offer many other operations, such as merging or joining of spatial data, extraction of values from one dataset into another, raster resolution changes, or vector data simplifications.
A comprehensive collection of methods to aggregate raster values to a coarser resolution can also be found in the *grainchanger* package \cite{Graham2019}.
Furthermore, *landscapetools* is a collection of various utility functions for the raster data model.

>>>>

A second common spatial data processing task is required when the available data extends over a larger area than the study region.
In this case, the pre-processing of spatial data should include vector clipping or raster cropping.
Related to that, masking certain areas of the study region can be required by using, e.g., certain spatial filters such as water bodies.
Packages from Section \@ref(sec:spatrep) also allow for these operations.
Additionally, they offer many other operations, such as merging or joining spatial data, extracting values from one dataset into another, raster resolution changes, or vector data simplifications.
A comprehensive collection of methods to aggregate raster values to a coarser resolution can also be found in the *grainchanger* package \cite{Graham2019}.
Furthermore, *landscapetools* is a collection of various utility functions for the raster data model \cite{Sciaini2018}.
